---
title: "Williams_Celeste-and-Shah-Pratik-ADA-Homework-04"
author: "C. Williams and P. Shah"
date: "4/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(curl)
library(dplyr)
library(sciplot)
```

```{r kam and cooper}
f <- curl("https://raw.githubusercontent.com/difiore/ADA-2019/master/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
d<- as_tibble(d)
head(d)
```

####[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).
```{r lm}
m<-lm(data = d, log(HomeRange_km2)~ log(Body_mass_female_mean))
summary(m)
m$coefficients
```

####[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the appropriate coefficients. This generates a sampling distribution for each β coefficient. Plot a histogram of these sampling distributions.
```{r bootstrapping}
c<-NULL
n<- length(d$Body_mass_female_mean)
for (i in 1:1000) {
  a<- d[sample(nrow(d),size=n, replace = TRUE),]
  b<- lm(data=a, log(a$HomeRange_km2)~ log(a$Body_mass_female_mean))
  c[i]<- list(b$coefficients)
}
head(c)
h<-do.call(rbind,c)
h<- as.data.frame(h)
colnames(h)<- c("Beta_0","Beta_1")
head(h)
hist(h$Beta_0)
hist(h$Beta_1)
```

####[3] Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap.

*Standard Error of Beta 0*
```{r beta0 SD}
sd(h$Beta_0)
```
*Standard Error of Beta 1*
```{r beta1 SD}
sd(h$Beta_1)
```

####[4] Also determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

*CI for Beta 0*
```{r CI beta0}
quantile(h$Beta_0, c(0.025, 0.975))
```
*CI for Beta 1*
```{r CI beta1}
quantile(h$Beta_1, c(0.025, 0.975))
```

####[5] How does your answer to part [3] compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
SE Estimate from entire dataset= Intercept/Beta0= 0.6729, Beta1= 0.08488
```{r both se}
sd(h$Beta_0)
sd(h$Beta_1)
```
These Standards Errors are very similar to each other.

#####[6] How does your answer to part [4] compare to the 95% CI estimated from your entire dataset?
```{r CI entire dataset}
alpha<- 0.05
mCI<- confint(m, level = 1-alpha)
mCI
quantile(h$Beta_0, c(0.025, 0.975))
quantile(h$Beta_1, c(0.025, 0.975))
```
The 95% Confidence Intervals are very similar. 

